Modeling potential JCPOA diversion scenarios with Cyclus

### 2018-05-15 paper.tex
mention no decay
formating

The plutonium, required for \glspl{MOX} fabrication, is reprocessed from all
used fuel.  At first , it is sourced only from UOX, then used MOX fuel as it becomes
available for reprocessing.

@@

In this works, a time step of 1 month have been considered.

@@

\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.35]{power_full}
    \caption{Electric power generated as a function of time.  The black line
        represents the reference calculation and the blue zone
        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:power_full}
\end{figure}

>>>>

The plutonium, required for \glspl{MOX} fabrication, is reprocessed from all
used fuel.  At first , it is sourced only from \glspl{UOX}, then used MOX fuel
as it becomes available for reprocessing.

@@

In this works, a time step of 1 month have been considered, i.e. each output
metrics are reported one each month and decay process have not be taking into
account.

@@

\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.36]{power_full}
    \caption{Electric power generated as a function of time.  The black line
        represents the reference calculation and the blue zone
        represents the 1 $\sigma$ uncertainty distribution.}\label{fig:power_full}
\end{figure}
